\documentclass[10pt,letterpaper]{article}
\usepackage[top=1.5cm, bottom=2cm, left=1.5cm, right=1.5cm]{geometry}

\title{AI Final Project}
\author{Stephen Olsen\\saolsen@uwm.edu}

\begin{document}
\maketitle

\subsection*{Introduction}
A Wikipedia race is a competition between two or more people where given a
start page and a goal page you try to get to get to the end page as quickly
as possible by clicking on internal wikipedia links. For an example and to try
it out see http://www.wikipediarace.com/

This project is my attempt at an application that tries to find the shortest
path between two wikipedia pages via links, as length of path is probably the
greatest determinate of how quickly one can move from the start page to the
goal.\\

\begin{description}
    \item[AI Algorithm:] Breadth first search.
    \item[Input:] A starting page and a goal page.
    \item[Output:] A List of the links in order to get from the start to the
                   end. 
    \item[Programming Language:] Python
    \item[Environment:] It will run on both Windows and Unix 
\end{description}

\subsection*{Description}
Takes a start page and a goal page as input. It them does a Breadth first search to
determine the shortest distance in links that it takes to get to the next page.
It filters out non real pages (like categories and wikipedia internal pages) but
does not stop untill it finds the goal. If there isn't a path it wont tell you so
untill it has exhaused whatever strongly connected component it started on (which
can take a very long time). For best results pick two common pages with lots of links.\\

\subsection*{Sample Usage}
\begin{description}
    \item Enter start page: Monk
    \item Enter goal page: FIFA
    \item link1
    \item link2
    \item link3
    \item .............
    \item ['Monk', 'England', 'FIFA']
\end{description}

\end{document}
